% System Development and Methodology

The proposed system will be developed using the Agile Software development methodology, \citep{agilemanifesto}.

\begin{enumerate}
      \item Concept


            Select the project idea to work on. This project was selected by identifying a gap in the market.

      \item Inception


            Set up the team that will develop the software. Provide the necessary tools and resources.

            Create Designs of the user interface and mockups and develop the project architecture.

      \item Iteration


            Develop and deploy the minimum functionality as fast as possible. Then iterate the process.

      \item Release

            Test the system and then release it.

      \item Maintenance

            Fix any issues identified in production

      \item Retirement

            Archive the system.
\end{enumerate}

Agile Software Development methodology is built on twelve principles:-

\begin{enumerate}
      \item Customer satisfaction by early and continuous delivery of valuable software.
      \item Welcome changing requirements, even in late development.
      \item Deliver working software frequently (weeks rather than months)
      \item Close, daily cooperation between business people and developers
      \item Projects are built around motivated individuals, who should be trusted
      \item Face-to-face conversation is the best form of communication (co-location)
      \item Working software is the primary measure of progress
      \item Sustainable development, able to maintain a constant pace
      \item Continuous attention to technical excellence and good design
      \item Simplicity—the art of maximizing the amount of work not done—is essential
      \item Best architectures, requirements, and designs emerge from self-organizing teams
      \item Regularly, the team reflects on how to become more effective, and adjusts accordingly
\end{enumerate}
